---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pmxcv

<!-- badges: start -->
<!-- badges: end -->

This package is intended to provide easy access to methods of reporting CV% in non-lognormal, non-normal distributions. Often in pharmacometric literature, CV% is only reported for lognormal variability (or treated as lognormal), favoring reporting of the harder-to-interpret variance parameter; this package attempts to provide an alternative approach.

## Installation

You can install the development version of pmxcv like so:

``` r
devtools::install_github("pfizer-rd/pmxcv")
```

## Example

Example of a typical use case:

```{r example}
library(pmxcv)

## Parameters from NONMEM (etc)
theta_bio <- 0.689
omega_bio <- 1.2

# Representation of bioavailability calculation in NONMEM syntax:L
# LOGITF1 = LOG( THETA(BIO) ) - LOG( 1 - THETA(BIO) )
# F1 = 1/( 1 + 1/EXP( LOGITF1 + ETA(BIO) )

## Numeric parameter variability
eta_sample <- rnorm(10^9, sd=sqrt(omega_bio))
logit_theta <- log(theta_bio) - log( 1 - theta_bio )
indiv_bios <- 1 / ( 1 + 1/exp( logit_theta + eta_sample ) )
expected_cv <- 100*sd(indiv_bios)/mean(indiv_bios)
expected_cv

## Lognormal reported CV% (erroneous)
bio_cv_lnorm <- 100*sqrt(exp(omega_bio) - 1)
bio_cv_lnorm

## Logitnormal reported CV%
bio_cv_lgtnorm <- dist.intcv("logit", u=theta_bio, v=omega_bio)
bio_cv_lgtnorm # should be approximately equal to numeric

```
